\documentclass{ltxguidex}
\usepackage{changelog}
\usepackage{fontspec}
\setmainfont{Charter}[
  Extension = .otf,
  UprightFont = * Regular,
  ItalicFont = * Italic,
  BoldFont = * Bold,
  BoldItalicFont = * Bold Italic,
]
\usepackage{FiraSans}
\usepackage{FiraMono}

\newcommand{\reqopt}[1]{Requires the \texttt{\color{magenta}#1} option.\par}
\usepackage{hologo}
\usepackage[quotes]{rebeccastyle}
\newacronyms{mla,}
\newcommand{\fontspecok}{\hologo{XeLaTeX} or \hologo{LuaTeX}}
\newcommand{\re}{\ltxclass{rebeccaessay}}
\newcommand{\rs}{\package{rebeccastyle}}
\title{The \rs\ package and the \re\ document class}
\author{Rebecca Turner\thanks{Brandeis University; \email{rebeccaturner@brandeis.edu}}}
\date{${VERSION}$}
\begin{document}
\maketitle

\begin{abstract}
	\re\ is a document class extending \ltxclass{article} for
	\fontspecok\ typeset in Garamond, with \mla\ citations via
	\hologo{BibTeX}, variable line spacing, and a |coverletter|
	environment.

	\re\ is, as the name implies, mostly intended for personal use.
\end{abstract}

\tableofcontents
\vfill
\pagebreak

\section{Package options}

By default, \rs\ does very little; additional features are opted into with
package options. Unless otherwise noted, an option can be explicitly
declined by prefixing it with |no|; for example, |bib| is disabled with
|nobib|.

\begin{keys}
	\key{geometry}
	Loads \ctan{geometry} and sets 1-inch margins. Enabled by default.

	\key{maketitle}
	Redefines |\maketitle| to be prettier, provides the |\heading| and
	|\essayintro| commands. Enabled by default.

	\key{titles}
	Loads \ctan{titlesec} and provides better section formats. Enabled by
	default.

	\key{headers}
	Loads \ctan{fancyhdr} and sets better page headers. Enabled by default.

	\key{hyperref}
	Loads \ctan{hyperref} Enabled by default.

	\key{shorthands}
	Provides command shorthands. Enabled by default.

	\key{tabu}
	Loads table packages \ctan{multirow}, \ctan{booktabs}, and
	\ctan{tabu}.

	Makes the |\Th| command available.

	\key{figures}
	Loads \ctan{graphicx} and \ctan{caption}, makes figure captions
	prettier.

	\key{lists}
	Loads \ctan{enumitem}.

	\key{footnotes}
	Loads \ctan{footmisc} and makes footnotes prettier.

	\key{quotes}
	Redefines the |quote| and |quotation| environments to add an
	optional argument.

	\key{bib}
	Sets up the document for an \mla-cited bibliography using Biber.
	Loads \ctan{biblatex}, \ctan{csquotes}, and \ctan{babel}.

	Makes the |\fullcite| command available.

	\key{coverletter}
	Make the |coverletter| environment and the |\address| command
	available.

	\key{fonts}
	Loads \ctan{fontspec} and \ctan{gillius}.

	\key{times}
	Sets the font to Times New Roman. This option has no negative form.

	\key{garamond}
	Sets the font to Garamond Premier Pro. Note that \option{garamond}
	is the default when the \option{font} option is given.

	\key{1}
	\key{1.5}
	\key{2}
	Controls leading with the \ctan{setspace} package. These options
	have no negative forms (e.x.\ \option{no1}).

	\begin{note}
		The \option{1} option differs from the default in that it
		loads the \package{setspace} package and calls
		|\singlespace|.
	\end{note}
\end{keys}

\section{The \re\ document class}
Using the \re\ document class is mostly equivalent to
\begin{latexcode}
\documentclass[12pt]{article}
\usepackage[fonts, footnote, quote, bib]{rebeccastyle}
\end{latexcode}

However, the default options can be overridden; passing \option{nobib} will
result in no bibliography system being loaded.

Unknown class options are passed to \ltxclass{article}.

\section{Commands}
\subsection{Starting the essay}

\begin{desc}
|\newacronym[<command>]{<acronym text>}|\\
|\newacronyms{<acronym list>}|\\
= |\ac| \qquad (With \option{shorthands} option.)
\end{desc}

Creates a new acronym. If |<command>| isn't given, the text of the macro
will be used instead; |\newacronym{mla}| would create |\mla|. If the
resulting command already exists, this will explode. For |\newacronyms|, the
|<acronym list>| is a comma-delimited list of acronyms.

\begin{LTXexample}
\newacronym[\xyz]{mla}
\xyz

\newacronym{ussr}
The \ussr\ was\dots
\end{LTXexample}

\begin{desc}
|\email{<email address>}|\\
|\emailstyle{<email address>}|
\end{desc}

Prints an email address with a |mailto:| link. The address is printed in
|\emailstyle|, which may be a command accepting one argument.

\begin{desc}
|\rebeccasetup{<options>}|
\end{desc}

Sets up general options. |<options>| can include:
\begin{keys}
	\key{street}[\m{street}]
	\key{city}[\m{city}]
	\key{phone}[\m{phone}]
	\key{email}[\m{email}]
	Address information, used in cover letters. Note that these keys are
	useless without the \option{coverletter} option.

	\key{author}[\m{author}]
	Shortcut for |\author{<author>}|.

	\key{headername}[\m{headername}]
	The name used in page headers. \mla\ requires only a surname, so it
	may be appropriate to set your surname here.

	\key{instructor}[\m{instructor}]
	The course instructor. Used in the \mla\ |\essayintro| command.

	\key{course}[\m{course}]
	The course number. Used in the \mla\ |\essayintro| command.
\end{keys}

\begin{desc}
|\heading|
\end{desc}
An \mla\ essay heading with the course instructor, course, and date.
Generally, users will want to use |\essayintro| instead.

\begin{desc}
|\essayintro|
\end{desc}
A combination of |\heading| and |\maketitle|.

\subsection{Other commands}

\begin{desc}
|\address|
\end{desc}
\reqopt{coverletter} Prints the address flush-right.

\begin{desc}
|\begin{coverletter}{<options>}...\end{coverletter}|
\end{desc}
\reqopt{coverletter} A cover letter, beginning with an |\address| and ending
with a signature. |<options>| must include \option{to}.
\begin{keys}
	\key[note=Mandatory]{to}[\m{recipient}]
	Person the letter is addressed to.

	\key{author}[\m{author}]
	The letter author. Actually a shortcut for |\author{<author>}|.

	\key{dear}[\m{text}][\{\}]
	Text in the style of ``dear\dots'' placed before the recipient's
	name.

	\key{signature}[\m{text}][Sincerely,]
	Signature text like ``Sincerely,'' or ``Love,'' prepended to the
	author's name.
\end{keys}

\begin{desc}
|\Th[<column spec>]{<header text>}|
\end{desc}

\reqopt{tabu} Typesets a table header in bold-face. |<column spec>| defaults
to |l|. Useful for when a column is wrapped in a math environment.

\begin{desc}
|\begin{quote}[<options>]...\end{quote}|\\
|\begin{quotation}[<options>]...\end{quotation}|\\
\end{desc}

\reqopt{quote} A wrapper around the original |quote| and |quotation|
environments which adds support for sources. |<options>| may include:
\begin{keys}
	\key{author}[\m{author}]
	The quote's author.

	\key{source}[\m{source}]
	The quote source. If the \option{author} option is also given, the
	source is printed in parenthesis.

	\key{cite}[\m{bib key}]
	A citation key. If given, |\textcite{<bib key>}| is used for the
	attribution. If given with \option{source} or \option{author}, may
	lead to unexpected results.
\end{keys}

\begin{desc}
|\fullcite{<bib key>}|
\end{desc}

\reqopt{bib} Prints a full citation as it will appear in the bibliography.

\begin{changelog}[author=Rebecca Turner]
\begin{version}[v=0.2.0, date=2019-10-15]
\changed
  \item Renamed |\intro| to |\essayintro| to avoid a conflict with the
    \ctan{knowledge} package.
  \item Build now uses \href{https://github.com/casey/just}{\texttt{just}} instead of
  |make|.
\fixed
  \item Fixed options being spelled incorrectly in documentation.
\end{version}
\end{changelog}
\end{document}
